Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
move running example section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Running Example} \label{sec:running-ex}

Using an optimisation tool, the work in~\cite{DBLP:conf/hybrid/WangGRJF16}
has designed a high-performance controller, which is characterised by the
following z-domain transfer function:
%
\begin{equation}
\label{Eq:running-example-controller}
C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}
%
The authors claim that this controller $C(z)$ stabilizes the closed-loop
system for the discrete plant model $G(z)$.  However, if implementation
aspects are considered during verification ({\it e.g.}, fixed-point
arithmetic and word-length), then this closed-loop system becomes unstable.
%
Indeed, the actual implementation of $C(z)$ using \param{4}{16}
implementation format ({\it i.e.}, $4$ bits for the integer part and $16$
bits for the fractional part) can be represented by the following
expression:
%
\begin{equation}
\label{Eq:running-example-controller-quantized}
C_{q}\left(z\right) {:=} \frac{2.719986z^2{-}4.153000z
{+}1.895996}{z^2{-}1.843994z+0.849594},
\end{equation} 
%
which makes the system unstable in closed-loop using fixed-point arithmetic
and the typical series loop configuration, where $C_{q}\left(z\right)$ and
$G\left(z\right)$ are in the forward path.

@@

\subsection{Program synthesis for the running example}
We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
We start with the candidate solution with all coefficients zero 
given below at $I_b=16,F_b=24$.
Note that the digital controller is designed with typical control system
techniques \cite{Kuo:2002:ACS:579453,Ogata:1987:DCS:26170}.
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.

>>>>

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Illustrative Example} \label{sec:running-ex}

Using an optimisation tool, the work in~\cite{DBLP:conf/hybrid/WangGRJF16}
has designed a high-performance controller, which is characterised by the
following z-domain transfer function:
%
\begin{equation}
\label{Eq:running-example-controller}
C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}
%
The authors claim that this controller $C(z)$ (Eq.~\eqref{Eq:running-example-plant}) 
stabilizes the closed-loop system for the discrete plant model $G(z)$ (Eq.~\ref{Eq:running-example-controller}).  
However, if implementation aspects are considered during verification ({\it e.g.}, fixed-point
arithmetic and word-length), then this closed-loop system becomes unstable.
%
Indeed, the actual implementation of $C(z)$ using \param{4}{16}
implementation format ({\it i.e.}, $4$ bits for the integer part and $16$
bits for the fractional part) can be represented by the following
expression:
%
\begin{equation}
\label{Eq:running-example-controller-quantized}
C_{q}\left(z\right) {:=} \frac{2.719986z^2{-}4.153000z
{+}1.895996}{z^2{-}1.843994z+0.849594},
\end{equation} 
%
which makes the system unstable in closed-loop using fixed-point arithmetic
and the typical series loop configuration, where $C_{q}\left(z\right)$ and
$G\left(z\right)$ are in the forward path.

\subsubsection{Program synthesis for the illustrative example}
We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
We start with the candidate solution with all coefficients zero 
given below at $I_b=16,F_b=24$.
Note that the digital controller is designed with typical control system
techniques \cite{Kuo:2002:ACS:579453,Ogata:1987:DCS:26170}.
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.
